%% Work Experience

\section{Work Experience}

\cventry{2009--Present}{Science Research Specialist}{Philippine Institute of Volcanology and Seismology (PHIVOLCS)}{}{}{%
\begin{itemize}
\item Process GNSS and geophysical data for tectonic monitoring, earthquake research, and fault assessment across the Philippines.
\item Design and build headless processing pipelines, distributed task systems, and full-stack applications (e.g., MOVE Faults, EIL Hazard Suite, PHAST) to automate decades of legacy scientific workflows.
\item Participate in GNSS field surveys and network maintenance, supporting station integrity and data continuity.
\item Contribute as co-author to peer-reviewed publications on crustal deformation and geodetic methods.
\item Transitioned technical skills to modern web development, building production applications that apply scientific rigor (TDD, strict data integrity) to software engineering.
\end{itemize}
}

\vspace{0.5em}

\cventry{2005--2009}{Software Test Engineer}{Azeus Systems Philippines}{}{}{%
\begin{itemize}
\item Performed functional and regression testing for large-scale web applications, including government contract platforms.
\item Wrote detailed manual test cases and reported issues with clear reproduction steps, improving dev handoff quality.
\item Used SQL for test setup and validation of back-end logic and edge cases during integration testing.
\end{itemize}
}

\vspace{0.5em}

\cventry{2004--2005}{Science Information Analyst}{ESS Manufacturing Company, Inc. (EMCI)}{}{}{%
\begin{itemize}
\item Indexed and summarized physics and engineering articles for an international scientific publication database.
\item Applied technical reading and abstract writing skills under tight deadlines across multiple disciplines.
\end{itemize}
}

\vspace{0.5em}

\cventry{2002--2003}{Student Assistant}{National Institute of Physics -- UP Diliman (Theoretical Physics Group)}{}{}{%
\begin{itemize}
\item Maintained Linux workstations for basic network access, file management, and local simulations.
\item Helped students troubleshoot command-line issues, particularly Fortran compilation and plotting with gnuplot.
\item Assisted with recovering and digitizing legacy scientific code from non-machine-readable sources.
\end{itemize}
}