%% Production Applications

\cventry{2024--Present}{PipetGo -- B2B Laboratory Testing Marketplace}{\textit{Next.js 14 · TypeScript · Prisma · NextAuth · PostgreSQL}}{}{}{%
Production MVP connecting businesses with ISO 17025 accredited testing labs.
\begin{itemize}
\item Implements multi-tiered pricing modes (QUOTE\_REQUIRED, FIXED, HYBRID) and multi-role authorization workflows.
\item Undergoing User Acceptance Testing with initial partner organizations before pilot deployment.
\end{itemize}
\textbf{Repository:} \url{https://github.com/alfieprojectsdev/pipetgo}
}

\vspace{0.5em}

\cventry{2024--Present}{PHAST -- PHIVOLCS Hazard Assessment Tool}{\textit{Vanilla JS · Chrome Extension API · Leaflet.js}}{}{}{%
Chrome Extension command center that injects professional GIS controls into standard web maps.
\begin{itemize}
\item Dynamically generates formatted, official hazard assessment text directly from map interactions.
\item Replaces manual text authoring for hazard assessors.
\end{itemize}
\textbf{Repository:} \url{https://github.com/alfieprojectsdev/phat}
}

\vspace{0.5em}

\cventry{2023--Present}{Window Cards Generator}{\textit{Vanilla JS · HTML5 · CSS3 · Print CSS}}{}{}{%
Zero-dependency Vanilla JS constraint-solving engine that dynamically generates printable math problem grids.
\begin{itemize}
\item Designed for SPED and early-grade classrooms with limited device access/connectivity.
\end{itemize}
\textbf{Live Demo:} \url{https://alfieprojectsdev.github.io/windowcards}
}

\vspace{0.5em}

\cventry{2024}{ArtPortfolio -- Statically Generated CMS}{\textit{Astro · Static Site Generation · GitHub Pages}}{}{}{%
High-performance Astro CMS built for digital art commissions, optimized for minimal cognitive load and fast asset delivery with zero client-side JS by default.
\textbf{Repository:} \url{https://github.com/alfieprojectsdev/artportfolio}
}