%% Active Development Projects

\cventry{2024--Present}{MOVE Faults \& EIL Hazard Suite}{\textit{Python · Celery · React · FastAPI · Docker}}{}{}{%
\begin{itemize}
\item \textbf{MOVE Faults:} Flagship GNSS automation monorepo replacing legacy scripts. Features a Celery-backed distributed task queue, real-time NMEA TCP streaming, and an offline React field app.
\item \textbf{EIL Hazard Suite:} Decoupled geohazard system featuring a headless spatial processing engine (EIL-Calc) for landslide susceptibility scoring and a React visualizer (EIL-Viz) for ground-truth validation.
\end{itemize}
}

\vspace{0.5em}

\cventry{2024--Present}{Civic \& Utility Platforms}{\textit{Next.js 14 · TypeScript · PostgreSQL · Prisma / Drizzle}}{}{}{%
\begin{itemize}
\item \textbf{YAKAP-Link:} Civic tech POC with strict transaction constraints and dispensing guard logic to mitigate phantom claims in the PhilHealth medicine program.
\item \textbf{Homebase:} ADHD-optimized household command center with heuristics for anomaly detection, distributed notification loops, and multi-residence bill tracking.
\item \textbf{Washboard:} Contactless QR car wash booking system replacing manual pen-and-paper queue tracking with a real-time receptionist dashboard.
\end{itemize}
}

\vspace{0.5em}

\cventry{2024--Present}{Agentic Orchestrators (NightCoder \& SciWriter)}{\textit{Python 3.11+ · Ollama · Local LLMs · Shell Scripts}}{}{}{%
\begin{itemize}
\item \textbf{NightCoder:} ADR-to-patch automation engine utilizing local LLMs (deepseek-r1, qwen2.5-coder) to synthesize structured implementation plans and git-style patches.
\item \textbf{SciWriter:} Config-driven writing pipeline that converts research notes into structured drafts with refinement passes, terminology normalization, and LaTeX/Beamer export.
\end{itemize}
}

\vspace{0.5em}

\cventry{2024--Present}{Drive Archaeologist \& SIPAT}{\textit{Python · TypeScript · React · IndexedDB}}{}{}{%
\begin{itemize}
\item \textbf{Drive Archaeologist:} Python CLI for excavating legacy GNSS data. Detects RINEX files, flags MD5 duplicates, and generates safe migration scripts.
\item \textbf{SIPAT:} Open-source CAPI alternative for field researchers needing offline-first data collection, complex branching logic, and automated audio transcription.
\end{itemize}
}